\textit{MSF: Modulated Sub-graph Finder}

### 2018-08-09 MSF_Paper_FA.tex
Update MSF_Paper_FA.tex

To overcome this limitation, we developed a novel approach to identify
concertedly modulated sub-graphs in the global cell signaling network,
based on the DGEA results of all genes tested. Thereby, expression patterns
of genes are integrated according to the topology of their interactions and
allow potentially to read the flow of information from the perturbation
source to the effectors. The described software, named \texttt{Modulated
  Sub-graph Finder} (\texttt{MSF}) is freely available at
\url{https://github.com/MariamFarman/Modulated-SubGraph-Finder}.

@@

The EBOV infection experiments describe the course of infection at three
time-points 6, 24 and 48 hour post infection (hpi). For the earliest time
point at 6~hpi, three large modulated sub-graphs were identified with 41,
107, and 18 genes were identified, as well as two with less than 4 genes.
The modulated sub-graphs consist predominantly of cytokines, chemokines
(CXCL10, CCL8) and Interleukin genes (IL6, IL27, IL23).
IFNB1 and IFNA1 were both identified as two of the possible sources
in one of the sub-graph identified with 18 genes.
Most of the sources identified by \texttt{MSF} were
type~I interferon induced genes (Supplement material 6H).
At 24~hpi eight modulated sub-graphs were
identified with four main sub-graphs consisting
of 27, 101, 134 and 194 genes, others being smaller than 10 genes. IFNB1
and IFNA1 were identified as the two sources out of the total sources. For the last time-point 48~hpi,
six modulated sub-graphs were identified. Three of the sub-graphs were
less than nine genes and main sub-graphs had 122, 191 and 202 genes. IFNB1 was identified as one of the sources in
the most significantly modulated sub-graph (Supplment).

>>>>

To overcome this limitation, we developed a novel approach to identify
concertedly modulated sub-graphs in the global cell signaling network,
based on the DGEA results of all genes tested. Thereby, expression patterns
of genes are integrated according to the topology of their interactions and
allow potentially to read the flow of information from the perturbation
source to the effectors. The described software, named \texttt{Modulated
  Sub-graph Finder} (\texttt{MSF}) is freely available at
\url{https://github.com/Modulated-Subgraph-Finder/MSF}.

@@

The EBOV infection experiments describe the course of infection at three
time-points 6, 24 and 48 hour post infection (hpi). For the earliest time
point at 6~hpi, three large modulated sub-graphs were identified with 41,
107, and 18 genes were identified, as well as two with less than 4 genes.
The modulated sub-graphs consist predominantly of cytokines, chemokines
(CXCL10, CCL8) and Interleukin genes (IL6, IL27, IL23).
IFNB1 and IFNA1 were both identified as two of the possible sources
in one of the sub-graph identified with 18 genes.
Most of the sources identified by \texttt{MSF} were
type~I interferon induced genes (Supplement material 6H).
At 24~hpi eight modulated sub-graphs were
identified with four main sub-graphs consisting
of 27, 101, 134 and 194 genes, others being smaller than 10 genes. IFNB1
and IFNA1 were identified as the two sources out of the total sources. For the last time-point 48~hpi,
six modulated sub-graphs were identified. Three of the sub-graphs were
less than nine genes and main sub-graphs had 122, 191 and 202 genes. IFNB1 was identified as one of the sources in
the most significantly modulated sub-graph (Supplement).
